EBASE manuscript

### 2023-01-08 manu-draft.qmd
working on optex fig

Several conclusions can be made from the results in @fig-apasumdat based on the patterns of the $R^2$ values. Overall, the model was able to estimate the $a$ parameter with reasonable precision regardless of any of the prior distributions, whereas most of the variation was observed in the $r$ and $b$ parameters.  Changing the variance of the $a$ parameter had little effect on any of the comparisons.  Smaller variance of the prior distribution for the $r$ parameter generally contributed to lower $R^2$ for all parameters, with the precision being worse for the 7-day optimization period (e.g., the $a$ parameter).  Larger variance of the prior distribution for the $b$ parameter generally contributed to lower $R^2$ only for the gas exchange estimate (D), although this effect was minimized with the 7-day optimization period.  As such, the results suggest that the default prior distributions used in EBASE may be appropriate in some cases, but increasing the prior variance for $a$ and $r$ and decreasing the variance for $b$ will likely produce more optimal solutions.

>>>>

Several conclusions can be made from the results in @fig-apasumdat based on the patterns of the $R^2$ values. Overall, the model was able to estimate the $a$ parameter with reasonable precision regardless of any of the prior distributions, whereas most of the variation was observed in the $r$ (respiration, R) and $b$ parameters.  Changing the variance of the $a$ parameter had little effect on any of the comparisons.  Smaller variance of the prior distribution for the $r$ parameter generally contributed to lower $R^2$ for all parameters, with the precision being worse for the 7-day optimization period (e.g., the $a$ parameter).  Larger variance of the prior distribution for the $b$ parameter generally contributed to lower $R^2$ only for the gas exchange estimate (D), although this effect was minimized with the 7-day optimization period.  As such, the results suggest that the default prior distributions used in EBASE may be appropriate in some cases, but increasing the prior variance for $a$ and $r$ and decreasing the variance for $b$ will likely produce more optimal solutions. The actual model results for the best performing combination of prior distributions for the one-day and 7-day optimization is shown in @fig-optex (all results are averaged at the time-step of the optimization period for comparability).
